---
title: "awtools"
output:
  md_document:
    variant: markdown_github
---
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/0.1.0/active.svg)](http://www.repostatus.org/#active)

# awtools
A simple, distilled, #rstats theme used mainly on [www.austinwehrwein.com](https://austinwehrwein.com/)

The main theme is the <code>a_plex_theme</code> which the fonts are available from Google Fonts:

- [IBM Plex Mono](https://fonts.google.com/specimen/IBM+Plex+Mono) (plot title, legend)
- [IBM Plex Sans](https://fonts.google.com/specimen/IBM+Plex+Sans) (subtitle, captions, axis_text)

<code>a_dark_theme</code> shares mostly all the same elements of the main theme but the colors are adjusted to make a dark theme.

## Examples
####<code>a_plex_theme</code> features:
- grid: [TRUE/FALSE] turns off the main panel grids.
- noaxis: [TRUE/FALSE] turns off the axis of the plot, seen mainly in maps.
- emphasis: ['x','y','xy'] adds a bold to an axis title for emphasis. 

```{r include=FALSE,warning=FALSE}
library(awtools)
library(gcookbook)
library(ggplot2)
library(tidyverse)
library(ggridges)
library(extrafont)
library(pals)
```

##palettes
```{r warning=FALSE}
pal.bands(ppalette,mpalette,spalette,gpalette,labels = c('Primary','Flat','Secondary','Gray'))

```

An example using the <code>a_plex_theme</code> with the <code>a_flat_color</code> palette.

```{r warning=FALSE}
ggplot(heightweight,aes(x=heightIn,y=weightLb, color = factor(round(ageYear)))) + 
  geom_point() +
  a_plex_theme() +
  a_flat_color() +
  labs(
    title='Height and Weight',
    subtitle='Sample data of height inches and weight in pounds.',
    caption='Source: R Graphics Cookbook',
    color='Age'
  )
```

Example of <code>a_dark_theme</code> with the primary color palette.

```{r warning=FALSE}
ggplot(mtcars, aes(mpg, wt)) +
  geom_point(aes(color=factor(carb), size=drat)) +
  labs(x="Fuel efficiency (mpg)", y="Weight (tons)",
       title="Basic scatterplot example",
       subtitle="A demonstration",
       caption="This be a caption") + 
  a_primary_color() +
  a_dark_theme()
```
 
And a new <code>a_gray_color</code> and <code>a_gray_palette</code> which is a simple four color grays palette.

```{r warning=FALSE}
lax<-read_csv('https://raw.githubusercontent.com/awhstin/temperaturesv2/master/LAX-NCDC-2015-18.csv') %>% 
  filter(months(DATE)=='January')%>%
  mutate(year=format(DATE,'%Y'),
         month=factor(months(DATE), levels=rev(month.name)))

ggplot(lax, aes(x=TAVG, y=month, fill=year)) +
  geom_density_ridges(scale=.9, color=NA) +
  a_plex_theme(grid=FALSE) +
  a_gray_fill()
```

##Old 

The original <code>a_theme</code> uses fonts that can be found and downloaded from Google Fonts:

- [Roboto](https://fonts.google.com/specimen/Slabo+27px) (plot title, legend)
- [Open Sans](https://fonts.google.com/specimen/Open+Sans) (subtitle, captions, axis_text)
 
The new <code>a_robot_theme</code> uses fonts that can be found and downloaded from Google Fonts:

- [Roboto Slab](https://fonts.google.com/specimen/Roboto+Slab) (plot title, legend)
- [Roboto Light](https://fonts.google.com/specimen/Roboto) (subtitle, captions, axis_text)
 
The new <code>a_concert_theme</code> uses fonts that can be found and downloaded from Google Fonts:

- [Concert One](https://fonts.google.com/specimen/Concert+One) (plot title, axis_title)
- [Inconsolata](https://fonts.google.com/specimen/Inconsolata) (subtitle, captions, axis_text)
 
Here is a simple scatterplot with the original <code>a_theme</code>.
```{r message=FALSE, warning=FALSE}
ggplot(heightweight,aes(x=ageYear,y=heightIn, color=sex))+
  geom_point()+
  a_theme()+
  a_scale_color() +
  labs(title='Height by Age',
       subtitle='Sample data of height in inches by age in years.',
       caption='Source: R Graphics Cookbook')
```
 
<code>a_robot_theme</code> gets the name from the use of Roboto and Roboto Slab for the base and plot title fonts. 

```{r message=FALSE, warning=FALSE}
ggplot(heightweight,aes(x=heightIn,y=ageYear, color = factor(round(ageYear)))) + 
  geom_point() +
  a_robot_theme() +
  a_flat_color() +
  labs(
    title='Height and Age',
    subtitle='Sample data of height inches and age in years.',
    caption='Source: R Graphics Cookbook',
    color='Age'
  )
```

The <code>a_concert_theme</code> was developed for a more editorial style visualization. 

```{r message=FALSE, warning=FALSE}
ggplot(climate,aes(x=Year,y=climate$Anomaly10y, color=Source)) + 
  geom_line(size=.75) +
  a_concert_theme() +
  a_primary_color() +
  labs(
    title='Temperature Anomaly',
    subtitle='Anomaly in Celsius, smoothed over ten years',
    caption='Source: R Graphics Cookbook',
    y='Anomaly'
  )
```

