---
title: "awtools"
output:
  md_document:
    variant: markdown_github
  html_document:
    keep_md: true
---
# a_theme
A simple, distilled, #rstats theme used mainly on [www.austinwehrwein.com](https://austinwehrwein.com/)

My main theme now is the <code>a_plex_theme</code> which the fonts are available from Google Fonts:

- [IBM Plex Mono](https://fonts.google.com/specimen/IBM+Plex+Mono) (plot title, legend)
- [Open Sans](https://fonts.google.com/specimen/Open+Sans) (subtitle, captions, axis_text)

The original <code>a_theme</code> uses fonts that can be found and downloaded from Google Fonts:

- [Roboto](https://fonts.google.com/specimen/Slabo+27px) (plot title, legend)
- [Open Sans](https://fonts.google.com/specimen/Open+Sans) (subtitle, captions, axis_text)
 
The new <code>a_robot_theme</code> uses fonts that can be found and downloaded from Google Fonts:

- [Roboto Slab](https://fonts.google.com/specimen/Roboto+Slab) (plot title, legend)
- [Roboto Light](https://fonts.google.com/specimen/Roboto) (subtitle, captions, axis_text)
 
The new <code>a_concert_theme</code> uses fonts that can be found and downloaded from Google Fonts:

- [Concert One](https://fonts.google.com/specimen/Concert+One) (plot title, axis_title)
- [Inconsolata](https://fonts.google.com/specimen/Inconsolata) (subtitle, captions, axis_text)
 
## New Examples
####<code>a_plex_theme</code> features:
- grid: [TRUE/FALSE] turns off the main panel grids.
- noaxis: [TRUE/FALSE] turns off the axis of the plot, seen mainly in maps.
- emphasis: ['x','y','xy'] adds a bold to an axis title for emphasis. 

```{r include=FALSE,warning=FALSE}
library(awtools)
library(gcookbook)
library(ggplot2)
library(tidyverse)
library(ggridges)
```
```{r warning=FALSE}
groups<-unique(uspopage$AgeGroup)
uspopage<-uspopage%>%
  filter(uspopage$AgeGroup %in% head(groups,6))
ggplot(uspopage, aes(x=Year, y=Thousands, color=AgeGroup)) + 
  geom_line(size=1) +
  a_main_color() +
  scale_y_continuous(labels = scales::comma)+
  labs(title="Age distribution of population\nin the U.S., 1900-2002",
       subtitle="Example data from the R Graphics Cookbook.",
       caption="Source: R Graphics Cookbook") +
  a_plex_theme() +
  theme(legend.position="bottom")
```

A new update to the awtools package sees a new dark theme that is based on the main plex theme.

```{r warning=FALSE}
ggplot(uspopage, aes(x=Year, y=Thousands, color=AgeGroup)) + 
  geom_line(size=1) +
  a_main_color() +
  scale_y_continuous(labels = scales::comma)+
  labs(title="Age distribution of population\nin the U.S., 1900-2002",
       subtitle="Example data from the R Graphics Cookbook.",
       caption="Source: R Graphics Cookbook") +
  a_dark_theme() +
  theme(legend.position="bottom")
```
 
And a new <code>a_gray_color</code> and <code>a_gray_palette</code> which is a simple four color grays palette.

```{r warning=FALSE}
lax<-read_csv('https://raw.githubusercontent.com/awhstin/temperaturesv2/master/LAX-NCDC-2015-18.csv') %>% 
  filter(months(DATE)=='January')%>%
  mutate(year=format(DATE,'%Y'),
         month=factor(months(DATE), levels=rev(month.name)))

ggplot(lax, aes(x=TAVG, y=month, fill=year)) +
  geom_density_ridges(scale=.9, color=NA) +
  a_plex_theme(grid=FALSE) +
  a_gray_fill()
```

##Old examples
Here is a simple scatterplot with the original <code>a_theme</code>.
```{r echo=TRUE, message=FALSE, warning=FALSE}
ggplot(heightweight,aes(x=ageYear,y=heightIn,color=ageYear))+
  geom_point()+
  a_theme()+
  labs(title='Height by Age',
       subtitle='Sample data of height in inches by age in years.',
       caption='Source: R Graphics Cookbook')
```
 
Here is an example of the color palette.
```{r, echo=TRUE}
ggplot(uspopage, aes(x=Year, y=Thousands, fill=AgeGroup)) + 
  geom_area() +
  a_scale_fill() +
  scale_y_continuous(labels = scales::comma)+
  labs(title="Age distribution of population\nin the U.S., 1900-2002",
       subtitle="Example data from the R Graphics Cookbook.",
       caption="Source: R Graphics Cookbook") +
  a_theme() +
  theme(legend.position="bottom")
```

I also created a reverse of the color palette which is debuted along with the 'a_robot_theme'.
```{r, echo=TRUE}
ggplot(uspopage, aes(x=Year, y=Thousands, fill=AgeGroup)) + 
  geom_area() +
  a_reversed_fill() +
  scale_y_continuous(labels = scales::comma)+
  labs(title="Age distribution of population\nin the U.S., 1900-2002",
       subtitle="Example data from the R Graphics Cookbook.",
       caption="Source: R Graphics Cookbook") +
  a_robot_theme() +
  theme(legend.position="bottom")
```

Finally for work I compare 4 and 6 factors often so I created a stepped version of my color palette. 

I also created a reverse of the color palette which is seen below. There has been some work that requires a slightly more editorial style graph so here is also the debut of the 'a_concert_theme'. 
```{r, echo=TRUE}
groups<-unique(uspopage$AgeGroup)
uspopages<-uspopage%>%
  filter(uspopage$AgeGroup %in% head(groups,4))
ggplot(uspopages, aes(x=Year, y=Thousands, fill=AgeGroup)) + 
  geom_area() +
  a_step_fill() +
  scale_y_continuous(labels = scales::comma)+
  labs(title="Age distribution of population\nin the U.S., 1900-2002",
       subtitle="Example data from the R Graphics Cookbook.",
       caption="Source: R Graphics Cookbook") +
  a_concert_theme() +
  theme(legend.position="bottom")
```

Finally a little display of a new color palette. 
```{r}
groups<-unique(uspopage$AgeGroup)
uspopage<-uspopage%>%
  filter(uspopage$AgeGroup %in% head(groups,6))
ggplot(uspopage, aes(x=Year, y=Thousands, color=AgeGroup)) + 
  geom_line(size=1) +
  a_main_color() +
  scale_y_continuous(labels = scales::comma)+
  labs(title="Age distribution of population\nin the U.S., 1900-2002",
       subtitle="Example data from the R Graphics Cookbook.",
       caption="Source: R Graphics Cookbook") +
  a_concert_theme() +
  theme(legend.position="bottom")
```

